Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-01-15 RET_Hosts.tex
Updates from Overleaf

The host galaxy photometry for the sample of RETs is taken from the catalogue of \citet{Wiseman2020}, which was based upon deep coadds reaching $g$-band limiting magnitudes of 27.

>>>>

The host galaxy photometry for the sample of RETs is taken from the catalogue of \citet{Wiseman2020}, which is based upon deep coadds reaching $g$-band limiting magnitudes of 27.
